Title?

### 2016-08-30 draft.tex
Add files via upload

\documentclass[nofootinbib,aps,prd,preprint,superscriptaddress]{revtex4}
\usepackage{amsmath,graphicx,hyperref}
\usepackage{slashed}

@@

\subsection{Trapping limit}
The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova. With a large enough coupling, the new particles will thermalize and then they will be emitted from a spherical shell.  In this case the luminosity is given simply by the Steffan-Boltzmann law
\beq
\mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma,
\eeq
where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature. We can estimate $ r = 10$ km, since the density of the supernova drops drastically around that point. After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ 
\beq
T_A \le 9.586\rm\ MeV.
\eeq
That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = 2/3 $, and finding the temperature that corresponds to that optical depth. This is a somewhat involved calculation.
First, one needs a model for the density and temperature in the supernova. Following \cite{Dent:2012mx}, we assume 
\bea
\rho &=& \rho_p \left(\frac{R}{r}\right)^2,\\
T &=& T_R \left(\frac{R}{r}\right)^{n/3},
\eea
with $  \rho_p  = 3\times10^{14}\ {\rm g/cm}^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
\beq
\tau = \int_{r_x}^{\infty} \kappa \rho dr,
\eeq
where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean Rosseland opacity 
\beq
\frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A,
\eeq
where $ l_A $ is the mean free path.

@@

Having obtained an expression for $ \kappa $, we can now find the optical depth
	[note to self: rework the steps here; too confusing]
and the bound on the coupling is finally found by requiring  $ \tau_R(\epsilon,m_A) \le 2/3 $

@@

@@

>>>>

\documentclass[nofootinbib,aps,prd,preprint,superscriptaddress]{revtex4}
\usepackage{amsmath,graphicx,hyperref}
\usepackage{slashed}
\usepackage{epstopdf}

@@

\subsection{Trapping limit}
The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova. With a large enough coupling, the new particles will thermalize and then they will be emitted from a spherical shell.  In this case the luminosity is given simply by the Steffan-Boltzmann law
\beq
\mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma,
\eeq
where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature. We can estimate $ r = 10$ km, since the density of the supernova drops drastically around that point. After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ 
\beq
T_A \le 9.586\rm\ MeV.
\eeq
That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = 2/3 $, and finding the temperature that corresponds to that optical depth. This is a somewhat involved calculation.
First, one needs a model for the density and temperature in the supernova. Following \cite{Dent:2012mx}, we assume 
\bea
\rho &=& \rho_p \left(\frac{R}{r}\right)^n,\\
T &=& T_R \left(\frac{\rho(r)}{\rho_R}\right)^{1/3},
\eea
with $  \rho_p  = 3\times10^{14}\ {\rm g/cm}^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
\beq
\tau = \int_{r_x}^{\infty} \kappa \rho dr,
\eeq
where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean Rosseland opacity 
\beq
\frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A,
\eeq
where $ l_A $ is the mean free path.

@@

Having obtained an expression for $ \kappa $, we can now find the optical depth as follows: define a new quantity $ \tau_R = \kappa_R \rho_R R $. We then have 
\beq \kappa \rho R = \tau_R (\frac{\rho}{\rho_R})^2 (\frac{T_R}{T})^{3/2}  \eeq
This is combined with the expressions for the density and temperature as a function of r and plugged in to the integral expression for the optical depth to obtain 
\bea \tau_x &=& \int_{r_x}^{\infty} \tau_R (\frac{R}{r})^{3n/2} \\
 &=& \frac{\tau_r}{\frac{3n}{2}-1} (\frac{T_A}{T_R})^{(9/2-3/n)} \eea
and the bound on the coupling is finally found by requiring  $ \tau_x(\epsilon,m_A) \le 2/3 $

@@

The calculation is dependent on a number of constants. We chose the following values as roughly typical of supernovae: T, the temperature of the supernova core, was set to 30 MeV; r, the radius of the supernova core, to 1 km; $ R $, the distance at which decay products are trapped, to 10 km; $ \mathcal{L} $, the luminosity bound, to $ 10^{53} erg/s $; and $ \n_b $, the baryon number density in the supernova interior, to $ 1.79*10^{38} cm^{-3} $.

@@

\begin{figure}[h!]
\includegraphics[height=9cm]{ope_bound.eps}
\caption{CAPTION}
\end{figure}
